\chapter*{Workflows}
This section describes several of the workflows LOST will help to automate.

\section*{Travel Management}
LOST will provide visibility into when and where assets are moved through the Travel Management workflow. This workflow will enforce OSNAP asset management policy.
\subsection*{Workflow Steps}
\begin{enumerate}
\item A user in logistics creates a travel request and includes the assets to be transfered, the request is in the `unapproved' state.
\item The request is then forwarded to management for approval. All managers must approve for the travel request to move forward, the request moves to the `approved' state. Logistics and facilities managers may not approve their own requests.
    \begin{enumerate}
    \item Logistics manager at the source
    \item Logistics manager at the destination
    \item Facilities manager at the source
    \item Facilities manager at the destination
    \end{enumerate}
\item Logistics manager at the source facility adds the convoy transporting the assets to the travel request. The asset is now associated with both the facility and the convoy. The request is now in the `ready' state.
\item After loading onto the convoy, a user in logistics updates the request state to `in transit' and the asset is disassociated from the source facility and associated with the destination facility.
\item While in transit, logistics users associated with the convoy periodically update the request with current location and other notes.
\item When the asset is received at the destination facility, a facilities manager associated with the destination facility moves the travel request into the `received' state. The asset is disassociated with the convoy.
\end{enumerate}


\section*{Asset Location History}
LOST will provide features to reconstruct a time ordered location history of an asset.
\subsection*{Workflow Steps}
\begin{enumerate}
\item A Logistics Manager or Facility Manager selects an asset and make a request for asset history.
\item The report request is logged for auditing.
\item Logistics Manager approves the request. Logistics managers may not approve their own requests.
\item The approved request is logged for auditing.
\item The requesting logistics or facilities manager opens the report in LOST. Openning the report is logged.
\end{enumerate}
\subsection*{Additional Notes}
An asset history report may only be viewed once. If the request approval causes LOST to generate and store the report internally, the report must be deleted once opened.

A logistics and facilities managers should only be able to request history for assets currently located at facilities they are associated with.

Logistics and facilities managers should only be able to see the facilities they associated with. Facilities that a logistics or facilities manager is not associated with should be omitted in the report. For example:\\
An asset starts at $A$, is moved to $B$, and ends at $C$, $A \rightarrow B \rightarrow C$.
A Facilities manager associated only with facilities $A$ and $C$ would get a report indicating $A \rightarrow C$. Similarly, a facilities manager associated only with facilities $B$ and $C$ would get a report indicating $B \rightarrow C$. A facilities manager not associated with $C$ should not be able to see the asset to request the report on.


\section*{Asset Inventory Report}
LOST will provide features to report on currently housed assets.
\subsection*{Workflow Steps}
\begin{enumerate}
\item A Logistics Manager or Facility Manager selects a facility and requests a report on assets currently located there.
\item The report request is logged for auditing.
\item Facilities Manager approves the request. Facilities managers may not approve their own requests.
\item The approved request is logged for auditing.
\item The requesting logistics or facilities manager opens the report in LOST. Openning the report is logged.
\end{enumerate}
\subsection*{Additional Notes}
An asset inventory report may only be viewed once. If the request approval causes LOST to generate and store the report internally, the report must be deleted once opened.

Logistics and facilities managers should only be able to request asset inventories for facilities they are associated with.

Logistics and facilities managers should only be able to see assets for which they have appropriate privileges. Assets the user does not have sufficient privilege for should be omitted if a substitution has not been given for the asset. For example:
An asset $I$ is in security compartments $A_{ts}$, $B_s$, and $C_u$. A user with $A_{ts}$, $B_{s}$, and $C_{u}$ will see the asset in the report since they have the correct compartments and sufficient clearance. A user with $A_{ts}$, $B_{ts}$, and $C_{ts}$ will see the asset in the report since they have the correct compartments and sufficient clearance. A user with compartments $A_s$, $B_s$, and $C_s$ should not see the asset $I$ since $A_{ts}$ exceeds their clearance. A user with compartments $A_{ts}$, $B_{ts}$, and $D_{ts}$ will not be able to see the asset since they are missing a required compartment.